### 2023-04-20 source/paper/main.tex
Just in case again...

\title{Arrest Rates and College Enrollment:
\texorpdfstring{\\}{} Examining the Impact of Two Federal Drug Control Acts}
\author{Ray Huang\thanks{Contact:
    \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
     I am grateful to Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback and guidance. I would also like to thank Alison Lodermeier and Francesco Ferlenga for their generous comments and support. A replication archive is available at https://github.com/rayhuang11/EconSeniorThesisRH.}
     \\Brown University, Honors Thesis}

@@

I use three separate research designs. The first and primary research design combats the endogeneity problem by leveraging variations in the intensity of drug arrests across different states. High-intensity states are defined as states with Black adult drug-related arrest rates above the 75th percentile two years before the passage of the federal drug act (e.g. for the Anti-Drug Abuse Act, 1984 was used.) I compare high-intensity states to low-intensity states, and I calculate both the first stage and reduced form estimates where the first stage is the impact of the act on Black adult drug-related arrest rates and the reduced form is the impact of the act on college enrollment. For additional supplemental analysis, I adapt the second and third research designs in \cite{britton2022} to estimate the impact of the federal drug acts on college enrollment at the individual level.

@@

I find that the Anti-Drug Abuse Act of 1986 had a modest impact on Black adult male arrest rates and a small negative impact on college enrollment. In addition, I find some evidence that an increase in Black adult drug-related arrest rates has a small negative impact on college enrollment rates. The Fair Sentencing Act of 2010 is harder to study due to substantial pretrends, and I find some evidence of a potentially positive impact on college enrollment for Black males. For my estimates to be considered causal, important pretrend and exclusion restrictions must be satisfied.

% Literature
This paper heavily builds upon recent work by \cite{britton2022}, who estimates the impact of the Anti-Drug Abuse Act on college enrollment and the impact of state-level legislation on college enrollment. She finds that "Black males had a 2.2 percentage point decrease in the relative probability of college enrollment after the passage of the Anti-Drug Abuse Act of 1986." I build upon her work by introducing a new counterfactual group that allows the impact to be split into a first-stage and reduced-form. I also introduce more modern and robust methods to deal with the issue of pretrends, and I spend some time replicating her results.

@@

My first and primary empirical approach looks at changes in college enrollment rates in high drug arrest states relative to the low drug arrest states before and after the passage of both the 1986 and 2010 acts where high drug arrest states are defined as states above the 75th percentile two years before the passage of the federal law \footnote{For the Anti-Drug Abuse Act of 1986, states with high Black adult normalized arrest rates include CT, DC, GA, IL, MD, MA, MO, NJ, NY, and TN. States with high Black juvenile normalized arrest rates include AR, CT, DE, DC, ME, MD, MA, MT, NJ, SD, and TN. For the Fair Sentencing Act of 2010, states with high Black adult normalized arrest rates include AL, AR, DE, DC, GA, KY, LA, MD, MS, MO, NJ, NC, TN, and VA. States with high Black juvenile normalized arrest rates include AL, DE, DC, GA, IL, KY, LA, MD, MS, MO, NJ, NC, PA, and SC. Note that states without any UCR Program drug arrest data are omitted from this analysis. See figure \ref{fig:heatmap} for a heatmap of high-intensity states in 1984.}. I primarily rely on data on adult arrests instead of juvenile arrests due to effect sizes and issues with pretrends \footnote{As discussed in the introduction, \cite{aizer} finds that juvenile incarceration has a larger impact on education than adult incarceration. However, since states with high adult arrests tend to have high juvenile arrest rates, my estimates are robust to which arrest rate is used.}. I examine the first-stage impact where the outcome is the change in drug-related arrest rates and the reduced-form impact where the outcome is college-enrollment. The first stage is evaluated using an event-study model that allows me to assess the evolution of relative outcomes while controlling for fixed differences across states and national trends over time. Using data at the state ($s$) by year ($t$) level, I estimate:

@@

where $\alpha_s$ and $\gamma_t$ are individual and time fixed effects, $X'_{st}$ is a vector of control variables, and $\epsilon_{st}$ represents a shock uncorrelated with the policy. The coefficients $\{\beta_m \}^{M}_{m=-G}$ summarize the magnitude of the dynamic effects and are displayed in an event-study plot \footnote{Since the Anti-Drug Abuse Act was passed in October, I normalize the $\beta$ in 1986 to be zero. Similarly, since the Fair Sentencing Act of 2010 was passed in August, I normalize the $\beta$ on 2010 to be zero.}. When testing for pre-trends, if the first-stage arrest rates are trending similarly before the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010, I expect the coefficients associated with pre-periods to be small and statistically insignificant.

@@

To address issues of low power associated with event study tests for pre-trends in both the first stage and reduced form regressions, I implemented suggestions from \cite{roth2022}, which include calculating the slope of a linear violation of parallel trends that a pre-trends test would detect a specified fraction of the time, the expected value of the coefficients conditional on passing the pre-test under the hypothesized trend, and useful statistics such as power, Bayes Factor, and likelihood ratio.

Overall, examining both the first-stage and reduced-form impact of the federal has the advantage of enabling me to estimate the impact of arrest rates on college enrollment for Black males. I conduct an instrumented difference-in-differences (DDIV) estimate where the endogenous variable is arrest rates and the instrument is an indicator for living in a high-intensity state. I follow the advice given in \cite{ddiv}. For my DDIV estimates to be causal, the exclusion restriction must be satisfied, i.e. it must be the case that college enrollment is only impacted through changes in arrest rates.  I report the DDIV estimator as the simple ratio of means, and I also calculate the DDIV estimator via two-stage least squares (2SLS). If the exclusion restriction is satisfied, then my estimate applies to populations whose arrest rate was increased by the federal drug act. To check whether my estimates may be affected by the weak-instrument problem, I report F-statistics.

@@

Finally, I also include a triple difference-differences specification, where the first difference is pre and post-time periods, the second difference is race, and the third difference is living in a high or low-Black drug arrest state. The identifying assumption for the triple difference is

@@

In all the regression specifications, I estimate the equation using ordinary least squares (OLS). I also follow the recommendations outlined in \cite{duflo_did} and report heteroskedasticity-robust standard errors that are clustered at the state level. All analyses use CPS October supplement final person weights and limit the sample to Black males aged 18-24 at the time of the passage of the federal act.

@@

It is important to note that the UCR data has several limitations. First and foremost, many counties failed to report their arrest rates for certain years. Secondly, the UCR's hierarchical reporting system requires that only the most severe crime be recorded in cases of multiple offenses, which may skew the data. Finally, variations in reporting practices among different law enforcement agencies, as well as changes in reporting standards over time, can affect the consistency and comparability of the data. Notably, in my sample, in certain years, one state failed to report any arrest data, which resulted in all persons living in said state being dropped from the analysis \footnote{Approximately 10,000 observations per year were dropped, which was less than 10\% of the total sample.}. Further, arrest data from Florida is missing from many years, particularly in years relevant to the Fair Sentencing Act of 2010. This is likely to bias our estimates downwards, as Florida has high rates of drug use and sales \footnote{Florida is the epicenter of the recent prescription drug epidemic in the United States \citep{lee}, and most Colombian cocaine was initially transported to the United States through the Caribbean and Florida \citep{williams}.}.  What does the criminology literature have to say on the matter? \cite{gove} conclude that the personal characteristics of the offender have minor effects on whether the crime is reported and that the UCR is a valid indicator for serious crimes. \cite{lynch} conclude that "missing data are substantial in the UCR program and certainly worthy of attention. They are not randomly distributed and cannot, therefore, simply be ignored. Much of the work done with the unimputed UCR data has overrepresented the experience of larger urban places and underrepresented smaller and less urban places (LaFree, 1998). It is difficult to determine if this overrepresentation has substantial effects on conclusions based on these data. The imputation strategies employed by the UCR program are reasonable and appear to reduce the overrepresentation of larger places. However, these methodologies can clearly be improved upon." Notably, there were a few observations in certain years that were extreme outliers. For example, the 99th percentile was 142 arrests in a certain state year, but the outlier would have over 1000 arrests. To deal with these extreme outliers (which are very likely to be erroneous), I implement a 95\% right tail winsorization \footnote{I use winsorization over trimming because it is likely the case that the outliers still belong to the distribution.}.

@@

Tables 1 and 2 report sample means separately for the pre and post-periods of both the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010. Table 1 uses the CPS-UCR linked dataset (which drops unmerged observations), while Table 2 uses the CPS dataset only. Comparing Table 1 to Table 2 provides a rough test for evaluating whether the states with missing UCR data certain years in are substantially different from the state without missing data. The number of observations is slightly smaller in the CPS-UCR merged dataset, except for the 2010-2016 period which is much smaller (likely due to the missing UCR data from Florida). The "enrolled in college" row is approximately identical between Table 1 and Table 2, and the proportion of Blacks and males is also largely the same.

Looking at Table 1, in all periods, about 15\% of the sample is Black.

Overall, my summary statistics table is similar to the one presented in \cite{britton2022}, but there are some minor differences.

@@

@@

In this section, I evaluate the impact of the Anti-Drug Abuse Act of 1986. In the next section, I discuss the Fair Sentencing Act of 2010.

@@

The results are presented in figure \ref{fig:ab_es_1986}, figure \ref{fig:jb_es_1986}, and table (XYZ).

For Black adults, using the event study model detailed in \ref{eq:state_level_es}, I find an increase in drug-related arrest rate associated with the Anti-Drug Abuse Act with gains between 3.08 and 12.71 arrests per 100,000 during each post-expansion year. Using the difference-in-difference model specified in \ref{eq:did}, I find a statistically significant increase of 45.13 arrests per 100,000. The estimates for years 2 and 3 after the expansion are larger than the estimates for years 1 and 4, indicating that the effect of the law took some time to "kick in", and the effect potentially decreased in later years.

To check for pretrends, in my event study model, I test the joint null hypothesis that all of the pretreatment event study coefficients are zero through an F-test, which I report at the bottom of each event study figure. In this case, in figure \ref{fig:ab_es_1986}, I get a $p$-value of 0.50, which increases my confidence in the parallel trends assumption. I additionally included plots of raw outcomes over time in figure  \ref{fig:raw_college_highlowab_1986}. As an additional robustness check, I implement suggestions from \cite{roth2022} in figure \ref{fig:pretrends_roth} \footnote{Using Roth's R package "pretrends", I calculate statistics about the power of the pre-test against the hypothesized trend. I calculate the power defined as the probability that I would find a significant pretrend under the hypothesized pretrend, the Bayes Factor defined as the ratio of the probability of failing to reject the pretest under the hypothesized trend relative to under parallel trends, and the likelihood ratio which is defined to be the ratio of the likelihood of the observed coefficients under the hypothesized trend relative to under parallel trends.}. Overall, the results imply that if there exists a pretrend, a quadratic pretrends is more worrying than the linear pretrend, as I have less power to detect a significant pretrend and the likelihood ratio is much higher.

@@

\subsubsection{Reduced Form Estimates}

The results are presented in figure \ref{fig:reducedform_ab}, figure \ref{fig:reducedform_jb}, and table (XYZ).

Notably, in Table 2 when examining a simple difference in means, the difference in college enrollment rates between pre and post-period for high and low-intensity states for Black adult drug-related arrests is -2.3\%, which matches the result in \cite{britton2022}

@@

The second stage DDIV results are presented in Table 3. Overall, I find a small negative effect of arrest rates on college enrollment in all three 2SLS specifications; however, the coefficients are small and statistically insignificant with large standard errors. If I scale the variables up, my estimate (with fixed effects and control variables) implies that if the arrest rate increased by 1000 Black Adult drug-related arrests per 100,000, then the college enrollment rate would decline by approximately 2.5 persons.

To test for the weak-instrument problem, I also report F-statistics from the first-stage regression, following conventional advice from \cite{staiger1997precise}. In my case, I find an F-statistic ranging from 15.9 to 20.2, providing evidence that my estimates are not biased by the weak-instrument problem.

@@

\subsubsection{Robustness Checks}

@@

Notably, any effect is likely not due to the mandatory sentencing minimum, but rather, is due to the overall lightening of sentences / prosecutions. \cite{ussc} found that

@@

I find that the first empirical strategy leveraging variation between high and low-intensity states is not an appropriate research design for studying the impact of the Fair Sentencing Act of 2010 on drug-related arrest rates. The results of the event study regressions specified in equation \ref{eq:state_level_es} can be found in figures XYZ. The coefficients provide strong evidence of significant pretrends in arrest rates before the passage of the Fair Sentencing Act.

@@

\subsubsection{Robustness Checks}

@@

estimates are downards biased -cps and ucr missing key data

@@

Other ideas for future research include exploring the impact of state-level policies on arrest rates and educational outcomes. \cite{britton2022} uses differences in marijuana laws, and future research can leverage other drug laws while introducing modern methods such as synthetic control designs.
synthetic control methods, etc
other datasets e.g. ACA
better arrest data, county/metropolitan level
other outcomes

@@

\begin{appendices}
  \section{Data}
  I include a summary statistics table for the CPS data that is not merged with the UCR program data.

  \section{Additional Results}
  The contents...
  \section{First stage arrest rate estimates}
  I include tables for the equation \ref{eq:state_level_es} estimates presented in figures XYZ.

@@

  \section{Reduced form college enrollment estimates}
  I include tables for the equation \ref{eq:state_level_es} estimates presented in figures XYZ.

@@

\end{appendices}

>>>>

\title{Arrest Rates and College Enrollment:
\texorpdfstring{\\}{} Examining the Impact of Two Federal Drug Control Acts}
\author{Ray Huang\thanks{Contact:
    \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
     I am grateful to Peter Hull for serving as my advisor and for providing me with fantastic feedback and guidance. I would also like to thank Alison Lodermeier and Francesco Ferlenga for their generous comments and support. A replication archive is available at https://github.com/rayhuang11/EconSeniorThesisRH.}
     \\Brown University, Honors Thesis}

@@

I use three separate research designs. The first and primary research design combats the endogeneity problem by leveraging variations in the intensity of drug arrests across different states. High-intensity states are defined as states with Black adult drug-related arrest rates above the 75th percentile two years before the passage of the federal drug act (e.g. for the Anti-Drug Abuse Act, 1984 was used). When examining Figure \ref{fig:raw_ab}a, it seems like the rise in arrest rates in high-intensity states started increasing at a faster pace. I compare high-intensity states to low-intensity states, and I calculate both the first stage and reduced form estimates where the first stage is the impact of the act on Black adult drug-related arrest rates and the reduced form is the impact of the act on college enrollment. For additional supplemental analysis, I adapt the second and third research designs in \cite{britton2022} to estimate the impact of the federal drug acts on college enrollment at the individual level.

@@

I find evidence that the Anti-Drug Abuse Act of 1986 had a modest impact on Black adult male arrest rates and a small negative impact on college enrollment. In addition, I find some evidence that an increase in Black adult drug-related arrest rates has a small negative impact on college enrollment. The Fair Sentencing Act of 2010 is harder to study due to substantial pre-trends \footnote{When looking Figure \ref{fig:raw_ab}b, there does not seem to be a change in arrest rates after the passage of the Fair Sentencing Act, suggesting that any results may be driven by pre-trends. I will formalize this finding in the results section.}, but I find some evidence of a potentially positive impact on college enrollment for Black males. For my estimates to be considered causal, important pre-trend and exclusion restrictions must be satisfied.

% Literature
This paper heavily builds upon recent work by \cite{britton2022}, who estimates the impact of the Anti-Drug Abuse Act on college enrollment and the impact of state-level legislation on college enrollment. She finds that "Black males had a 2.2 percentage point decrease in the relative probability of college enrollment after the passage of the Anti-Drug Abuse Act of 1986." I build upon her work by introducing a new counterfactual group that allows the impact to be split into a first stage and reduced form. I also introduce more modern and robust methods to deal with the issue of pre-trends, and I spend some time replicating her results.

@@

My first and primary empirical approach looks at changes in college enrollment rates in high drug arrest states relative to the low drug arrest states before and after the passage of both the 1986 and 2010 acts where high drug arrest states are defined as states above the 75th percentile two years before the passage of the federal law \footnote{For the Anti-Drug Abuse Act of 1986, states with high Black adult normalized arrest rates include CT, DC, GA, IL, MD, MA, MO, NJ, NY, and TN. States with high Black juvenile normalized arrest rates include AR, CT, DE, DC, ME, MD, MA, MT, NJ, SD, and TN. For the Fair Sentencing Act of 2010, states with high Black adult normalized arrest rates include AL, AR, DE, DC, GA, KY, LA, MD, MS, MO, NJ, NC, TN, and VA. States with high Black juvenile normalized arrest rates include AL, DE, DC, GA, IL, KY, LA, MD, MS, MO, NJ, NC, PA, and SC. Note that states without any UCR Program drug arrest data are omitted from this analysis. See figure \ref{fig:heatmap} for a heatmap of high-intensity states in 1984.}. I primarily rely on data on adult arrests instead of juvenile arrests due to effect sizes and issues with pre-trends \footnote{As discussed in the introduction, \cite{aizer} finds that juvenile incarceration has a larger impact on education than adult incarceration. However, since states with high adult arrests tend to have high juvenile arrest rates, my estimates are robust to which arrest rate is used.}. I examine the first stage impact where the outcome is the change in drug-related arrest rates and the reduced form impact where the outcome is college-enrollment. The first stage is evaluated using an event-study model that allows me to assess the evolution of relative outcomes while controlling for fixed differences across states and national trends over time. Using data at the state ($s$) by year ($t$) level, I estimate:

@@

where $\alpha_s$ and $\gamma_t$ are individual and time fixed effects, $X'_{st}$ is a vector of control variables, and $\epsilon_{st}$ represents a shock uncorrelated with the policy. The coefficients $\{\beta_m \}^{M}_{m=-G}$ summarize the magnitude of the dynamic effects and are displayed in an event-study plot \footnote{Since the Anti-Drug Abuse Act was passed in October, I normalize the $\beta$ in 1986 to be zero. Similarly, since the Fair Sentencing Act of 2010 was passed in August, I normalize the $\beta$ on 2010 to be zero.}. In each event-study plot I also include the difference between the average of the post-period and pre-period coefficients; to account for potential pre-trends, I also report the average of the post-period coefficients, which is equivalent to the average treatment effect on the treated (ATT). When testing for pre-trends, if the first stage arrest rates are trending similarly before the passage of the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010, I expect the coefficients associated with pre-periods to be small and statistically insignificant.

@@

To address issues of low power associated with event study tests for pre-trends in both the first stage and reduced form regressions, I implemented suggestions from \cite{roth2022}, which include calculating the slope of a linear violation of parallel trends that a pre-trends test would detect a specified fraction of the time, the expected value of the coefficients conditional on passing the pre-test under the hypothesized trend, and useful statistics such as power, Bayes Factor, and likelihood ratio. If the parallel trends assumption is satisfied, then my first stage and reduced form estimates would identify the average treatment effect on the treated.

Overall, examining both the first stage and reduced form impact of the federal has the advantage of enabling me to estimate the impact of arrest rates on college enrollment for Black males. I conduct an instrumented difference-in-differences (DDIV) estimate where the endogenous variable is arrest rates and the instrument is an indicator for living in a high-intensity state. I follow the advice given in \cite{ddiv}. For my DDIV estimates to be causal, the exclusion restriction must be satisfied, i.e. it must be the case that college enrollment is only impacted through changes in arrest rates.  I report the DDIV estimator as the simple ratio of means, and I also calculate the DDIV estimator via two-stage least squares (2SLS). If the exclusion restriction is satisfied, then my estimate applies to populations whose arrest rate was increased by the federal drug act. To check whether my estimates may be affected by the weak-instrument problem, I report F-statistics.

@@

Finally, for supplemental analysis, I also include a triple difference-differences specification in the appendix, where the first difference is pre and post-time periods, the second difference is race, and the third difference is living in a high or low-Black drug arrest state. If White men have a similar first stage pre-trend to Black males in high vs low-intensity states, the triple difference-difference specification will remove that bias from that specific pre-trend.

@@

In all the regression specifications, I estimate the equation using ordinary least squares (OLS). I also follow the recommendations outlined in \cite{duflo_did} and calculate heteroskedasticity-robust standard errors that are clustered at the state level. All analyses use CPS October supplement final person weights and limit the sample to Black males aged 18-24 at the time of the passage of the federal act.

@@

It is important to note that the UCR data has several substantial limitations. First and foremost, many counties failed to report their arrest rates for certain years. Secondly, the UCR's hierarchical reporting system requires that only the most severe crime be recorded in cases of multiple offenses, which may skew the data. Finally, variations in reporting practices among different law enforcement agencies, as well as changes in reporting standards over time, can affect the consistency and comparability of the data. Notably, in my sample, in certain years, one state failed to report any arrest data, which resulted in all persons living in said state being dropped from the analysis \footnote{Approximately 10,000 observations per year were dropped, which was less than 10\% of the total sample.}. Further, arrest data from Florida is missing from many years, particularly in years relevant to the Fair Sentencing Act of 2010. This is likely to bias our estimates downwards, as Florida has high rates of drug use and sales \footnote{Florida is the epicenter of the recent prescription drug epidemic in the United States \citep{lee}, and most Colombian cocaine was initially transported to the United States through the Caribbean and Florida \citep{williams}.}.  In the criminology literature, \cite{gove} conclude that the personal characteristics of the offender have minor effects on whether the crime is reported and that the UCR is a valid indicator for serious crimes. \cite{lynch} conclude that "missing data are substantial in the UCR program and certainly worthy of attention. They are not randomly distributed and cannot, therefore, simply be ignored. Much of the work done with the unimputed UCR data has overrepresented the experience of larger urban places and underrepresented smaller and less urban places (LaFree, 1998). It is difficult to determine if this overrepresentation has substantial effects on conclusions based on these data. The imputation strategies employed by the UCR program are reasonable and appear to reduce the overrepresentation of larger places. However, these methodologies can clearly be improved upon." Notably, there were a few observations in certain years that were extreme outliers. For example, the 99th percentile was 142 arrests in a certain state year, but the outlier would have over 1000 arrests. To deal with these extreme outliers (which are very likely to be erroneous), I implement a 95\% right tail winsorization \footnote{I use winsorization over trimming since it is likely the case that the outliers still belong to the distribution.}.

@@

Tables 1 and A1 (in the appendix) report sample means separately for the pre and post-periods of both the Anti-Drug Abuse Act of 1986 and the Fair Sentencing Act of 2010. Table 1 uses the CPS-UCR linked dataset (which drops unmerged observations), while Table 2 uses the CPS dataset only.

Comparing Table 1 to Table A1 provides a rough test for evaluating whether the states with missing UCR data certain years in are substantially different from the state without missing data. The number of observations is slightly smaller in the CPS-UCR merged dataset, except for the 2010-2016 period which is much smaller (likely due to the missing UCR data from Florida). The "enrolled in college" row is approximately identical between Table 1 and Table 2, and the proportion of Blacks and males is also largely the same.

In Table 1, in all periods, about 15\% of the sample is Black. The total proportion of males enrolled in college fluctuates heavily, but the proportion of Black males enrolled in college is more stable, as most of the fluctuations in total male college enrollment are driven by non-Black males. Overall, my summary statistics in Table 1 and A1 are similar to the one presented in \cite{britton2022}, but there remain minor differences.

In figure \ref{fig:heatmap} I presented a heatmap of Black adult drug-related arrests in 1984, two years before the passage of the Anti-Drug Abuse Act. I also present kernel density estimates of the distribution of arrest rates at the state level in figure \ref{fig:density_jb} with a vertical line denoting high-intensity states.

@@

In the first subsection, I first evaluate the impact of the Anti-Drug Abuse Act of 1986, broken down into the first stage, reduced form, and second stage. In the next subsection, I discuss the Fair Sentencing Act of 2010.

For important event-study figures, I include tables in the appendix with all the coefficients of interest.

@@

@@

The first stage results are presented in figures \ref{fig:ab_es_1986}, \ref{fig:ab_es_1986_nofe}, \ref{fig:jb_es_1986}, table 2, and table A2 in the appendix.

For Black adults, using the event study model detailed in equation \ref{eq:state_level_es}, I find an increase in drug-related arrest rate associated with the Anti-Drug Abuse Act with gains between 3.08 and 12.71 arrests per 100,000 during each post-expansion year. When using the event-study model specified in equation \ref{eq:state_level_es}, I find that the average between the post and pre-period coefficients is 2.96, and the ATT is a bit larger at 3.85 arrests with a similar standard error. The estimates for years 2 and 3 in the post-period are larger than the estimates for years 1 and 4, 5, and 6, indicating that the effect of the law took some time to "kick in", and the effect potentially decreased in the later years \footnote{I confirmed that the large standard errors in certain post-periods were not due to coding errors by regressing the outcome in said year minus outcome in year zero on the treatment group.}. If I omit fixed effects from the event-study model (in Figure \ref{fig:ab_es_1986_nofe}), the event-study model estimates a larger and statistically significant effect, where the difference between the post and pre-periods is 7.1 with a robust, clustered standard error of 2.5. Similarly when using the difference-in-difference model specified in equation \ref{eq:did}, I find a statistically insignificant increase of approximately 3.3 arrests per 100,000.

To check for pre-trends in my event study model, I test the joint null hypothesis that all of the pretreatment event study coefficients are zero through an F-test, which I report at the bottom of each event study figure. In this case, in figure \ref{fig:ab_es_1986}, I get a $p$-value of 0.27, which increases my confidence in the parallel trends assumption. I additionally included plots of raw outcomes over time in Figure \ref{fig:raw_college_highlowab_1986}. As an additional robustness check, I implement suggestions from \cite{roth2022} in figure \ref{fig:pre-trends_roth} \footnote{Using Roth's R package "pre-trends", I calculate the power defined as the probability that I would find a significant pre-trend under the hypothesized pre-trend, the Bayes Factor defined as the ratio of the probability of failing to reject the pretest under the hypothesized trend relative to under parallel trends, and the likelihood ratio which is defined to be the ratio of the likelihood of the observed coefficients under the hypothesized trend relative to under parallel trends.}. The results from Roth's pre-trend package imply that if there exists a pre-trend, a quadratic pre-trends is more worrying than the linear pre-trend, as I have less power to detect a significant pre-trend and the likelihood ratio is much higher. Notably, if there exists a pre-trend, figure \ref{fig:ab_es_1986} suggests that the pre-trend is possibly negative, which would imply that my first stage estimates are biased downwards.

@@

\subsubsection{Reduced Form Estimates from High vs Low-Intensity States}

The results from comparing high to low-intensity states are presented in figure \ref{fig:rs_es_1986} and tables 4 and 5.

In figure \ref{fig:rs_es_1986}, I find that there is likely a pre-trend, as I calculate an f-statistic of 0.035. However, the pre-trend appears to be in the opposite direction of the effect, implying that if there existed a pre-trend, my model would underestimate the effect of the Anti-Drug Abuse Act on college enrollment, i.e. my estimate would be biased upwards. I calculate that the average between the post and pre-period coefficients is -0.0004, and the ATT is -0.02 which is equivalent to a 2\% decrease in the probability of enrollment, matching the estimate in \cite{britton2022}. Similar to the first stage, I find that the effect size increases at first in years 1, 2, and 3, then the effect stops increasing around year 4. Overall, I find my estimates reduced form estimates are quite noisy.

I also present simple difference-in-difference estimates of the treatment effect in tables 4 and 5. To increase power, I also calculated the same regression model, except I used continuous treatment (arrest rates) instead. My difference-in-difference estimates are consistent with the event-study results, as most are small, negative, and statistically insignificant.

@@

In table 2, I present a simple table of means without any controls or fixed effects to consolidate the results from the first stage and reduced form models. Notably, in table 2, when examining a simple difference in means, the difference in college enrollment probability between pre and post-period for high and low-intensity states for Black adult drug-related arrests is -2.3\%, which matches the result in \cite{britton2022} The instrumented difference in difference estimate from this table is equivalent the ratio between the reduced form and first stage, which is -0.2326/3.332 = -0.0698 = -6.9\%.

The more robust second stage DDIV results are estimated via 2SLS and are presented in table 3. Overall, I find a small negative effect of arrest rates on college enrollment in all three specifications; however, the coefficients are small and statistically insignificant with large standard errors. Notably, my 2SLS estimates are at least 10 times the magnitude of the OLS estimate (presented in column 1). If I scale the variables up, my most robust estimate (with fixed effects and control variables) implies that if the arrest rate increased by 1000 Black Adult drug-related arrests per 100,000, then the probability of college enrollment for a Black male would decline by approximately 2.5\%, once again, matching the estimate found in \cite{britton2022}.

To test for the weak-instrument problem, I also report F-statistics from the first stage regression, following conventional advice from \cite{staiger1997precise}. In my case, I find an F-statistic ranging from 15.9 to 20.2, providing evidence that my estimates are likely not biased by the weak-instrument problem.

@@

The results from the second and third empirical strategies (following the approach in \cite{britton2022}) are presented in tables 10 and 11. My estimates from using White males as a counterfactual group are similar to Britton's, except my estimates are a bit larger, with a decrease in the probability of college enrollment for Black males between 3.3\% and 5.7\%. When I use Black females as a counterfactual group, I find smaller, statistically insignificant estimates of approximately -1.6\%. To test for pre-trends, I plot the raw outcomes by treatment group overtime. These outcome figures can be found in the appendix.

@@

Notably, any effect is likely not due to the mandatory sentencing minimum, but rather, is due to the overall lightening of sentences / prosecutions. \cite{ussc} found that in the years before the Fair Sentencing Act was passed, the proportion in prison with minimum sentencing requirements was in the single digits.

@@

I attempt first to estimate the impact of the Fair Sentencing Act on drug-related arrest rates for Black adults and Black juveniles separately by looking at changes in arrest rates in high-drug arrest intensity states relative to the low-drug arrest intensity states before and after 2010.  I find that empirical strategy is not an appropriate research design for studying the impact of the Fair Sentencing Act of 2010 on drug-related arrest rates due to the failure of the parallel trends assumption. The results of the event study regressions specified in equation \ref{eq:state_level_es} can be found in figure \ref{fig:fs_es_2010}. The coefficients provide strong evidence of significant pre-trends in arrest rates before the passage of the Fair Sentencing Act, and the calculated f-statistics is essentially 0.

In this case, the pre-trend is trending in the same direction as the measured effect. I.e. my estimated effect is likely larger than the true effect. Using adult arrests, I find that the difference between the post and pre-period coefficients is -20.8, while the ATT is -22.8.

@@

The results from comparing high to low-intensity states are presented in figure \ref{fig:rf_jb_es_2010} and tables A4 and A5 in the appendix. Similar to the first stage result, I find significant pre-trends trending in the same direction as the effect. I conclude that comparing high and low-intensity states is not an approach research design for measuring the reduced form impact of the Fair Sentencing Act on the probability of college enrollment.

I next use White males as a counterfactual group to Black males, and the results are presented in table 14.

\subsubsection{Second Stage Estimate}

Due to significant pre-trends in both the first stage and reduced form estimates, I refrain from calculating a second stage estimate for the Fair Sentencing Act.

\subsection{Robustness Checks} %update to reflect both 1986 and 2010

I present numerous robustness checks.

For the first empirical strategy, I leverage variation in Black juvenile arrests as a robustness check. I calculated both the first-stage and reduced form, and the results are presented in figures \ref{fig:jb_es_1986} and \ref{fig:rs_es_1986}. Overall, I find that the estimates are similar between the models using adult arrest and the models using juvenile arrests. Using juvenile results tends to lead to smaller estimates, but at the same time, the pre-trends are potentially worse.

As a robustness check for the reduced form estimates from comparing high vs low-intensity states, I run the same regressions using Black juvenile arrests instead of Black adult arrests, and I present the results in tables 6 and 7.
I also run two separate control experiments in tables 8 and 9. In table 8, I limit my sample to females exclusively, and in table 8, I use Black males aged 30-50 in 1986. In both cases, I find very small, insignificant results.

For the second stage estimate, I include multiple regression specifications in table 3. My 2SLS estimates are somewhat robust to model specification; however, the effect size does increase when I add fixed effects and control variables.

To check the robustness of my additional reduced form estimates from using White males and Black females as counterfactual groups, I estimate the same model while restricting the sample to Males aged 30-50 in tables 12 and 13

@@

It is important to summarize and acknowledge several important issues this study faces.

First, many assumptions must be satisfied for the estimates presented in this paper to be interpreted as causal. For the first stage and reduced form estimates, the parallel trends assumption must be satisfied. For the instrumented difference in differences estimate to be causal, the exclusion restriction must be satisfied. While I include many checks for these assumptions, some more convincing than others, certain assumptions may still be invalid. In particular, I found that the Fair Sentencing Act was especially difficult to study due to failed parallel trend assumptions.

On the data side, the poor quality of the UCR program's arrest data may bias my estimates. Many counties failed to report arrest data, and it's highly unlikely that counties randomly failed to report data. Furthermore, since the population impacted by these Acts is so small, the CPS dataset may not be sufficiently powered to answer the research questions presented in this paper.

Finally, it may be the case that the subpopulation impacted by these Acts would not have attended college with or without the treatment. In other words, the local average treatment effect might have been 0, and in many instances, my estimates are very close to 0. However, it is unclear whether my estimates are small due to insufficient power and noise or the true local average treatment effect being 0.

@@

Other ideas for future research include exploring the impact of state-level policies on arrest rates and educational outcomes. \cite{britton2022} uses differences in marijuana laws, and future research can leverage other drug laws while introducing modern methods such as synthetic control designs.

other datasets e.g. ACA
better arrest data, county/metropolitan level
other outcomes

@@

\clearpage
\appendix
\section*{Appendix}
\beginsupplement

  \section{Data}
  I include a summary statistics table for the CPS data that is not merged with the UCR program data.

  \section{Additional Results}
  The contents...
  \section{First stage arrest rate estimates}
  I include a table (A2) for the equation \ref{eq:state_level_es} estimates presented in figure \ref{fig:ab_es_1986}.

@@

  \section{Reduced form college enrollment estimates}
  I include a table (A3) for the equation \ref{eq:state_level_es} estimates presented in figure \ref{fig:rs_es_1986}.

  Although it is likely the case that my estimates of the impact of the Fair Sentencing Act of 2010 using high vs low-intensity states is biased by significant pre-trends, in table A4 and A5 I include simple difference-in-difference estimates under three similar specifications; table A4 uses discrete treatment while table A5 uses continuous treatment. Overall my estimates imply a small negative effect on college enrollment probability, but my estimates are not sufficiently powered to be statistically significant.

  In tables A6-A8, I include the triple difference-in-differences results. I use both adult and juvenile arrests for the Anti-Drug Abuse Act, but I omit the juvenile table from the Fair Sentencing Act analysis since the pre-trends assumption is already quite weak. Counter to my previous results, when using adult arrest rates in the 1986 Act, I find a significant, positive effect on college enrollment. However, the significance drops away when I switch to juvenile arrests as a robustness check. Since the bias needs to be the same in each difference-in-difference estimate, if the parallel trends assumption is not satisfied, the triple difference-in-difference estimators may be more biased than my normal estimates.

@@

  % Fair Sentencing Act High/low intensity

  \import{../../output/tables/}{DiD_2010_high_low.tex}
  \begin{footnotesize}
    \noindent Note: Treated observations are defined as those living in states with a high-drug arrest rate for black adults, where high black adult drug arrest states are defined to be those above the 75th percentile in 2008. Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as males aged 18-24 in 1986 who were not incarcerated at the time of the survey.
  \end{footnotesize}

  \import{../../output/tables/}{DiD_2010_high_low_cont.tex}
  \begin{footnotesize}
    \noindent Note: Estimates are weighted using CPS October supplement weights. Robust standard errors are clustered at the state level. Controls: age, age-squared, Latino ethnicity, yearly state average unemployment rates, and (binned) family income. The sample is defined as males aged 18-24 in 2010 who were not incarcerated at the time of the survey.
  \end{footnotesize}
  \clearpage
